\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-18 paper/fse23/experiment.tex
debug

\paragraph*{\textbf{NLP Models \& Dataset}}
We evaluate our approach on three learning-based \sa models released from the Hugging Face centralized
model hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
language using a masked language modeling (MLM) objective, and
were fine-tuned on the \sa task. In this experiment, we used the \Sstt \cite{socher2013sst} dataset for
searching the seeds in \tool. \Sstt is a
corpus of movie review, consisting of 11,855 sentences
with sentiment scores. We split the
scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign them
negative, neutral and positive labels, respectively. In addition,
\Swn~\cite{baccianella2010sentiwordnet} is a publicly available dataset for English sentiment lexicons.  
It provides lexical sentiment scores and the sentiment word labels 
are categorized by implementing the rules.
We used \Swn as both the generation and the expansion domain knowledge as shown in Figure \ref{fig:overview}.

>>>>

\paragraph*{\textbf{NLP Models \& Dataset}}
We evaluate our approach on three learning-based \sa models released from the Hugging Face centralized
model hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
language using a masked language modeling (MLM) objective, and
were fine-tuned on the \sa task. In this experiment, we used the \Sst \cite{socher2013sst} dataset for
searching the seeds in \tool. \Sst is a
corpus of movie review, consisting of 11,855 sentences
with sentiment scores. We split the
scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign them
negative, neutral and positive labels, respectively. In addition,
\Swn~\cite{baccianella2010sentiwordnet} is a publicly available dataset for English sentiment lexicons.  
It provides lexical sentiment scores and the sentiment word labels 
are categorized by implementing the rules.
We used \Swn as both the generation and the expansion domain knowledge as shown in Figure \ref{fig:overview}.
